\clearpage
% \vspace*{4cm}
\section*{Acknowledgements}
%\vspace*{.5cm}

\indent I would like to thank my advisor, Aran Garcia-Bellido, without whom this work would not have happened. 
I thank him for always being available to help, but also for giving me the space to explore my own ideas. 
Without his trust and generosity I would have not spent the wonderful years I did at CERN. I am forever 
grateful to him. I'd like to thank Pablo Goldenzvweig for all the advice he gave me. It has been a great 
pleasure to have been associated with the faculty and staff of the University of Rochester. Connie, Laura, 
thank you for your dedication and vigilance that kept me on track! \\
\indent I am grateful to have worked with a great analysis team; thank you to (in no particular order): Ted Laird, 
Rob Bainbridge, Lucien Lo, Mark Baber, Henning Flaecher, Paris Sphicas, Jad Marrouche, Oliver Buchmueller, 
Bryn Mathias, Sam Rogerson, Darren Burton, Antonis Agapitos, Chris Lucas and Zhaoxia Meng. In some form or 
another they all contributed to this thesis and without their work it would not be what it is today. 
I would like to thank the supy development team, Burt Betchart, Davide Gerbaudo and Ted Laird for their contribution 
in creating such a wonderful analysis framework. My thanks go to the HCAL operations team, especially German 
Martinez who made me feel welcomed from day one and Sudan Paramesvaran for bringing a joyful spirit to HCAL.
I would like to thank Jared Sturdy for his patience when I interrupted his work to have him answer my questions! 
I'm forever grateful to Ted Laird. His help, advice, contributions to this thesis is immeasurable. This work is
heavily based on the framework he's built and the quality of his work has been an inspiration. I'd like to thank 
Mashalo, Richarou and the Laudato family for always being there for me. I would like to thank all my friends for 
the stories and laughs throughout the CERN years. \\
\indent I would like to thank Jennifer and Galen for welcoming me to their respective homes without
an ounce of hesitation, you are wonderful people. 
The love, encouragement and support from my parents, brother, and sister have gotten me to where I am today.
This thesis is dedicated to them. 
